Enhancement of SDR in Thessaloniki

### 2024-04-17 GHI_enh_03_process.tex
Commit 2024-04-11 12:14
Commit 2024-04-17 00:14
Commit 2024-04-17 09:13

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-08}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}

@@

C4 factor: 1.05 
C4 offset: 0 
\end{verbatim}

@@

@@

@@

@@

@@

\begin{verbatim}
2024-04-08 15:48:57.0 athan@sagan GHI_enh_02_ID_CE.R 29.123272 mins
\end{verbatim}

@@

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
dummy
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-08 15:55:25.5 athan@sagan GHI_enh_02_ID_CE.R 3.671820 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-04-16}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Warning in eval(ei, envir):

 ** Test is active!! ** 
\end{verbatim}

\begin{verbatim}
Warning: Invalid .internal.selfref detected and fixed by taking a (shallow)
copy of the data.table so that := can add this new column by reference. At an
earlier point, this data.table has been copied by R (or was created manually
using structure() or similar). Avoid names<- and attr<- which in R currently
(and oddly) may copy the whole data.table. Use set* syntax instead to avoid
copying: ?set, ?setnames and ?setattr. If this message doesn't help, please
report your use case to the data.table issue tracker so the root cause can be
fixed or this message improved.
\end{verbatim}

\begin{verbatim}
Cross over point: 2014.75 
\end{verbatim}

\begin{verbatim}
2024-04-16 15:13:21.3 athan@tyler GHI_enh_Aeronet.R 0.022648 mins

USING TRASPARENCY TREND

@@

C4 factor: 1.09 
C4 offset: 0 
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-2} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-3} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-4} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-5} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-6} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-7} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-8} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-9} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-10} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-11} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-12} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-13} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-14} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-15} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-16} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-17} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-18} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-19} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-20} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-21} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-22} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-23} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-24} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-25} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-26} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-27} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-28} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-29} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-30} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-31} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-32} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-33} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-34} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-105} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-106} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-107} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-108} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-109} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-110} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-111} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-112} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-113} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-114} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-115} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-116} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-117} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-118} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-119} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-120} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-121} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-122} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-123} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-124} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-125} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-126} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-127} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-128} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-129} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-130} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-131} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-132} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-133} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-134} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-135} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-136} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-137} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-138} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-139} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-140} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-141} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-142} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-143} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-144} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-145} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-146} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-147} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-148} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-149} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-150} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-151} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-152} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-153} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-154} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-155} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-156} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-157} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-158} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-159} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-160} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-161} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-162} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-163} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-164} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-165} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-166} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-167} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-168} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-169} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-170} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-171} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-172} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-173} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-174} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-175} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-176} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-177} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-178} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-179} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-180} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-181} \end{center}

\begin{verbatim}
Warning in eval(ei, envir): TEST IS ACTIVE !!
\end{verbatim}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_03_process_files/figure-latex/unnamed-chunk-4-182} \end{center}

  TEST IS ACTIVE  !!

2024-04-16 15:16:07.1 athan@tyler GHI_enh_Aeronet.R 2.786622 mins
\end{verbatim}

@@

\begin{verbatim}
aa
aday
AEin1
All_daily_ratio_lim
alpha
ampl
avar
b
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
C4_test_cs_ref_ratio
C4_test_GLB_diff_THRES
C4_test_lowcut_ratio
C4_test_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
dummy
Energy_Div
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
mid
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
RANDOM_SEED
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
zeropoint
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_sza_doy
ST_E_sza_monthly
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_SZA_doy
ST_extreme_SZA_monthly
ST_extreme_total
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_sza_doy
ST_sza_monthly
ST_total
ST_yearly
\end{verbatim}

@@

\begin{verbatim}
2024-04-16 15:30:24.9 athan@tyler GHI_enh_Aeronet.R 10.090148 mins
\end{verbatim}
